### 2021-06-24 setup.tex
another pass in the threats to validity section

\item What is the impact of the DroidFax static analysis algorithms on the results of the BLL-Study?
  We estimate the impact in terms of the number of detected malwares.

@@

To sum up, in order to analyse the
performance of the test case generation tools (including Joker),
we just have to compare the calls to sensitive APIs made by
the benign and malign versions of the apps, during
the execution of the tools. In the end, we generate
a set of observations, where each observation
contains the tool name, the number of the repetition (in the
range [1..3]), a boolean value reporting the use of the
DroidFax static analysis component, and a boolean value indicating
whether or not the malware has been identified. We use descriptive statistics
and plots to compare the performance of the tools and
answer RQ1 and RQ2. We also use \emph{Logistic Regression}~\cite[Chapter~4]{statistical-learning}
to understand the statistical relevance and
the contribution of each feature (tool, repetition, DroidFax static analysis
component) to malware identification.

@@

We use two metrics in this second study:
the total number of malicious apps FlowDroid is able to
find and the execution time for running the taint analysis algorithm
for each app. Similarly to the first empirical study,
we use descriptive statistics
and plots to compare the performance of the taint analysis and
mining sandbox approaches. We also use \emph{Logistic Regression}~\cite[Chapter~4]{statistical-learning}
to better understand the statistical
significance of the benefits of using FlowDroid
(in comparison to the DroidFax static analysis
component only).

>>>>

\item What is the impact of the DroidFax static analysis algorithms on the results of the \blls?
  We estimate the impact in terms of the number of detected malwares.

@@

To sum up, in order to analyse the
performance of the test case generation tools (including Joker),
we just have to compare the calls to sensitive APIs made by
the benign and malign versions of the apps, during
the execution of the tools. In the end, we generate
a set of observations, where each observation
contains the tool name, the number of the repetition (in the
range [1..3]), a boolean value reporting the use of the
DroidFax static analysis component, and a boolean value indicating
whether or not the malware has been identified. We use descriptive statistics
and plots to compare the performance of the tools and
answer RQ1 and RQ2. We also use \emph{Logistic Regression}~\cite[Chapter~4]{statistical-learning}
to understand the statistical relevance and
the contribution of each feature (tool, repetition, DroidFax static analysis
component) to malware identification. Our hypothesis here is that
the DroidFax static analysis component has a positive
effect on the performance of the sandboxes to identify malwares.

@@

We use two metrics in this second study:
the total number of malicious apps FlowDroid is able to
find and the execution time for running the taint analysis algorithm
for each app. Similarly to the first empirical study,
we use descriptive statistics
and plots to compare the performance of the taint analysis and
mining sandbox approaches. We also use \emph{Logistic Regression}~\cite[Chapter~4]{statistical-learning}
to better understand the statistical
significance of the benefits of using FlowDroid
(in comparison to the DroidFax static analysis
component only). Our hypothesis here is that
FlowDroid outperforms, in terms of the number of
detected malware, the sandbox generated
by the DroidFax static analysis component.

### 2021-06-24 threats.tex
another pass in the threats to validity section

Due to the randomization behavior presented by each chosen tool, we should not validate the results of this experiment without considering the presence of random events in the execution. To mitigate this, we have used a configuration of the benchmark DroidXP tool that runs multiple times each test and computes the average result from those executions. So, the comparison between the results of this experiment and the experiment presented by Bao et al. could be more precise.
Beyond that, we tested only 96 of the original 102 pairs of apps in this experiment because the benchmark could not execute those six pairs of apps due to crashes in the Android emulator. This difference threatens the validity of the comparison between the Bao et al.'s experiment and ours.

>>>>

As any empirical work, this work also has
limitations and threats to its validity. We
organize this section using the taxonomy
of Wohlin et al.~\cite[Chapter 8]{10.5555/2349018}.

\textbf{Conclusion Validity} is concerned with
the issues that might compromise the
correct conclusion about the causal relation
between the treatment and the outputs of an
experiment. The use of inadequate statistical
methods and low statistical significance
are examples of threats to the conclusion validity.
Besides using descriptive statistics and
plots, we also leverage
binomial logistic regression to support our conclusions
in our two empirical studies. Indeed, the results of our logistic
regression analysis give evidence about the existence
of a true pattern in the data, indicating that the DroidFax
static analysis component increases the performance of the sandboxes
we built from the execution of the dynamic
analysis tools (first study) and that FlowDroid outperforms
the DroidFax static analysis component in the
task of identifying malwares (second study).

\textbf{Internal Validity} relates to external factors that might
impact the independent variables without the researchers' 
knowledge. Our two empirical studies are \emph{technology-oriented}~\cite{10.5555/2349018,expruna},
which are not subject to learning effect threats. Nonetheless,
due to the random behavior of the test case generation tools,
we should not validate the results of this experiment without considering the presence of
random events in the execution. To mitigate this threat, we have used a configuration of
DroidXP that runs multiple times each tool and computes the average result
from those executions. So, we could adequately compare the results of our experiment with
the results of the \blls. Beyond that,
we tested only 96 of the original 102 pairs of apps in this experiment because the we
could not execute those six pairs of apps due to crashes in the Android emulator.
However, our goal here is not to conduct an exact replication of the previous work,
but actually to better understand how static analysis supports and complements
the mining sandbox approach for malware identification.

\textbf{Construct Validity} concerns possible issues that might
prevent a researcher to draw a conclusion from the experimental
results. The design of our first study involves one treatment
(a two-level factor indicating the use or not of the
DroidFax static analysis component) and three independent
variables: {\bf app id} (96 level factor), the test
case generation tool (4-level factor, including DroidBot,
DroidMate, Monkey, and Humanoid), and the 3-level factor repetition
(we executed every tool three times for all apps, with and without
the DroidFax static analysis component). The dependent variable
indicates if a malware has been identified by the sandbox
of a given test case generation tool built with (or without) the
DroidFax static analysis component (in a particular repetition). This
design leads to a total of 2304 observations, which is in conformance with the recommendations
of Arcuri and Briand~\cite{arcuri:icse11} for this kind of experiment.
Our second study presents a more straightforward design, comprising a two
factor treatment (FlowDroid x the DroidFax static analysis) and   
the same set of 96 apps of the first study. The dependent variable
indicates if a malware has been identified by FlowDroid
or by the sandbox the DroidFax static analysis component generates. This
design leads to a smaller number of runs,
but we still believe that it is sufficient to draw our conclusions
(as the results of the logistic regression indicate).

\textbf{External Validity} concerns whether or not the
researchers can generalize the results for different scenarios.
Our study shares some of the threats the
\blls had presented. In particular, here we used the same set of pairs of apps from a \emph{piggy-backed} dataset
released by Li et al.~\cite{li2017understanding}. That is, using this dataset, we could not
cover all categories of Android malware. Besides that, we only used a small number of four test
case generation tools in this study. To mitigate these threats and enrich
the generalization of our research, we make available DroidXP, which does allow future
experiments to evaluate other test case generation tools in different malware
datasets.
